Equation-free analysis of a dynamically evolving multigraph

### 2016-02-07 report/multigraph_manuscript.tex
Near perfect commit, everything seems to work if you can just find the right parameters (which I'll hopefully specify in an upcoming commit)

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.9\textwidth]{graph-evo}
  \caption{Illustration of the steps enumerated above that evolve the graph from $t$ to $t+1$ \label{fig:step-illustration}}
\end{figure}

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{erdos-init}
    \subcaption{Initial graph is an Erd\H{o}s-R\'{e}nyi random graph. \label{fig:erdos-init}}
  \end{subfigure} \\ %
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{lopsided-init}
    \subcaption{Initial graph is half completely connected, half isolted vertices. \label{fig:lopsided-init}}
  \end{subfigure}%
  \caption{Figure showing evolution of degree sequence over time. Despite starting from different initial configurations, both systems evolve to the same steady state. \label{fig:dse}}
\end{figure}

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.8\textwidth]{triangle-slaving}
  \caption{Figure showing evolution of triangle counts over time,
    starting from three different initial networks that shared the
    same degree sequence. Thus higher-order variables that may be
    initialized off the slow manifold are quickly drawn to it
    ($O(n^2)$ steps). \label{fig:sv}}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=1.1\textwidth]{cpi-diagram}
  \caption{A diagram of the CPI procedure developed for this system. \label{fig:cpi-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{cpi-3d-comp}
    \subcaption{Percent error for each vertex in a CPI-accelerated simulation compared to an ensemble of plain simulations. \label{fig:cpi-error}}
  \end{subfigure} \\ %
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{cpi-error-comp}
    \subcaption{Percent error when comparing two ensembles of plain runs, showing the discrepancies arising simply from the stochastic nature of the system. \label{fig:self-error}}
  \end{subfigure}%
  \caption{Figure showing small errors in CPI routine. \label{fig:cpi-results}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{newton-error}
    \subcaption{Evolution of error in the coarse Newton-GMRES scheme. \label{fig:newton-error}}
  \end{subfigure} \\ %
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{newton-comp}
    \subcaption{Visual comparison of the algorithm's solution to the stationary state arising from direct simulation. \label{fig:newton-comp}}
  \end{subfigure}%
  \caption{Performance of coarse Newton-GMRES routine. \label{fig:newton-results}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{pca-2d-rho}
    \subcaption{Coloring the two-dimensional PCA embedding with
      $\rho$. \label{fig:pca-rho}}
  \end{subfigure} \\ %%
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{pca-2d-kappa}
    \subcaption{Coloring the two-dimensional PCA embedding with
      $\kappa$. \label{fig:pca-kappa}}
  \end{subfigure}%
  \caption{Embedding of steady states in $\rho$ / $\kappa$ plane,
    showing that PCA can uncover the two-dimensional structure of the
    dataset. \label{fig:pca}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{dmaps-3d-convergence}
    \subcaption{Figure showing embedding of two trajectories on
      different timescales. Initially they are separate, but
      eventually they're embedded in the same region as they evolve to
      the same coarse stationary state. Initial and final states are
      circled, and point size grows as more steps are
      taken in each trajectory. \label{fig:dmaps-results-regular}}
  \end{subfigure} \\ %%
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{dmaps-3d-convergence-zoom}
    \subcaption{An enlarged view of the final points in the previous
      plot, revealing the approach to a similar final
      state. \label{fig:dmaps-results-zoom}}
  \end{subfigure}%
  \caption{One dimensional embedding of different trajectories with DMAPS. \label{fig:dmaps-results}}
\end{figure}

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{dmaps-2d-rho}
    \subcaption{Coloring the two-dimensional DMAPS embedding with
      $\rho$. \label{fig:dmaps-rho}}
  \end{subfigure} \\ %%
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{dmaps-2d-kappa}
    \subcaption{Coloring the two-dimensional DMAPS embedding with
      $\kappa$. \label{fig:dmaps-kappa}}
  \end{subfigure}%
  \caption{Embedding of steady states in $\rho$ / $\kappa$ plane,
    showing that DMAPS uncovered the variables governing the
    stationary state, known from
    Bal\'{a}zs' paper \label{fig:dmaps-rk}}
\end{figure}

>>>>

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.9\textwidth]{graph-evo}
  \caption{Schematic of the substeps of the evolution dynamics of the
    multigraph $G(t)$. \label{fig:step-illustration}}
\end{figure}

\begin{figure}[th!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{lopsided-degs-a}
    \subcaption{\label{fig:lopsided-init}}
  \end{subfigure} %
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{erdos-degs-a}
    \subcaption{\label{fig:erdos-init}}
  \end{subfigure}
  \caption{Multigraph evolution dynamics for an $n=100$ vertex graph
    observed through the degree distribution. Two distinct transients
    are shown, initialized with (a) an Erd\H{o}s-R\'{e}nyi random
    graph with $m = 5,050$ edges and (b) a graph in which half the
    vertices are isolated, and half completely connected among
    themselves. \label{fig:dse}}
\end{figure}

\begin{figure}[th!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{triangle-slaving}
    \subcaption{\label{fig:sv-n2}}
  \end{subfigure} %
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{triangle-slaving-n3}
    \subcaption{\label{fig:sv-n3}}
  \end{subfigure}
  \caption{Evolution of higher-order statistics (here, the total
    triangle count) for three different network initializations. They
    are quickly ($O(n^2)$ steps) drawn to a slow manifold on which
    they slowly evolve ($O(n^3)$ steps) to a steady
    state. \label{fig:sv}}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=\textwidth]{cpi-diagram}
  \caption{Schematic of our restriction ($R$) and lifting ($L$)
    procedures. The graph's sorted degree sequence is calculated
    ($R_1$) and then fit to a third-order polynomial ($R_2$). This
    maps graphs ($G$) to vectors of four coefficients
    ($\mathbf{c}$). To lift, the polynomial is used to generate a
    degree sequence ($L_1$), which is then used to construct a
    consistent graph ($L_2$). This process maps vectors of
    four coefficients ($\mathbf{c}$) to graphs
    ($G$). $R = R_2 \circ R_1 $ is our restriction and $L = L_2 \circ
    L_1$ is our lifting. \label{fig:cpi-diagram}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{cpi-3d-comp}
    \subcaption{\label{fig:cpi-error}}
  \end{subfigure} %
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{cpi-relative-error-n3}
    \subcaption{\label{fig:self-error}}
  \end{subfigure}%
  \caption{CPI results: (a) the evolution of the CPI-accelerated
    degree sequence (red) compared to direct simulation (blue) and (b)
    error in cpi-accelerated runs calculated by comparing
    cpi-accelerated degree sequences to those arising from an ensemble
    of direct simulations. \label{fig:cpi-results}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{newton-error}
    \subcaption{\label{fig:newton-error}}
  \end{subfigure} %
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{newton-comp}
    \subcaption{\label{fig:newton-comp}}
  \end{subfigure}%
  \caption{Coarse Newton-GMRES results: (a) evolution of error in the
    coarse Newton-GMRES scheme and (b) visual comparison of the
    algorithm's solution to the stationary state arising from direct
    simulation. \label{fig:newton-results}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{pca-2d-rho-a}
    \subcaption{\label{fig:pca-rho}}
  \end{subfigure} %
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{pca-2d-kappa-a}
    \subcaption{\label{fig:pca-kappa}}
  \end{subfigure}%
  \caption{PCA of motif-based embeddings: (a) coloring the
    two-dimensional PCA embedding with $\rho$ and (b) coloring the
    two-dimensional PCA embedding with $\kappa$. \label{fig:pca}}
\end{figure}

@@

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{dmaps-3d-convergence}
    \subcaption{\label{fig:dmaps-results-regular}}
  \end{subfigure} %
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{dmaps-3d-convergence-zoom}
    \subcaption{\label{fig:dmaps-results-zoom}}
  \end{subfigure}%
  \caption{DMAP of motif-based embeddings from two separate simulation
    trajectories: (a) embedding of two trajectories on different
    timescales. While the trajectories are initially embedded in
    separate regions due to their different initial conditions,
    they're eventually mapped close together as they evolve to the
    same coarse stationary state. Final states are circled, and point
    size grows as more steps are taken in each trajectory. (b)
    Enlarged view of the final points in the previous plot, revealing
    the approach to a similar final state. Here, the average of the
    final fifty points is circled. Due to the stochastic nature of
    the system, the final embeddings randomly fluctuate about the
    shared stationary state. \label{fig:dmaps-results}}
\end{figure}

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{dmaps-2d-rho-a}
    \subcaption{\label{fig:dmaps-rho}}
  \end{subfigure} %
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{dmaps-2d-kappa-a}
    \subcaption{\label{fig:dmaps-kappa}}
  \end{subfigure}%
  \caption{DMAP of motif-based embeddings from collection of different
    simulations run with different parameter values: (a) coloring the
    two-dimensional DMAPS embedding with $\rho$ and (b) coloring the
    two-dimensional DMAPS embedding with $\kappa$. As with PCA, DMAPS
    uncovered the variables governing the stationary state, known from
    Bal\'{a}zs' paper \label{fig:dmaps-rk}}
\end{figure}
